Supplementary materials

### 2020-01-10 manuscript/figs/etc/figures.Rmd
directory cleanup

asv_similarity <- include_graphics(here("manuscript/figs/main/taxonomy/asvs2.png"))
communities <- include_graphics(here("manuscript/figs/main/community/community_ggplot_polished_2.png"))
unifrac <- include_graphics(here("manuscript/figs/main/uf_plot.png"))
# depth <- include_graphics(here("manuscript/figs/depth_comparison/depth_fig.png"))

@@

heatmap_cap <- "Relative abundance heatmap of snow algae community composition using cell morphology, 18S, and \\emph{rbc}L. Samples on the x-axis are arranged from low to high elevation. Taxonomic designations for \\emph{rbc}L are based on \\emph{de novo} OTU clustering, while taxonomic assignments for 18S are reference-based. Samples lacking data for a particular dataset are shown as blank (e.g. G1.4 18S)."

@@

```{r rel_abund, fig.cap = heatmap_cap}
communities
```

>>>>

asv_similarity <- include_graphics(here("manuscript/figs/main/taxonomy/asvs2.png"))
communities <- include_graphics(here("manuscript/figs/stacked_barplot.png"))
unifrac <- include_graphics(here("manuscript/figs/main/uf_plot.png"))
# depth <- include_graphics(here("manuscript/figs/depth_comparison/depth_fig.png"))

@@

heatmap_cap <- "Stacked barplot showing relative abundance community composition using cell morphology, 18S, and \\emph{rbc}L. Taxonomic designations for \\emph{rbcL} are based on \\emph{de novo} OTU clustering, while taxonomic assignments for 18S are reference-based. Samples on the y-axis are arranged in order of elevation."

@@

```{r rel_abund, fig.cap = heatmap_cap, fig.width=6, fig.height=5}
communities
```

### 2020-01-10 manuscript/supp/etc/supplemental.Rmd
directory cleanup

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png")) # crop zoom, city font white, each site gets one point with box specifying elev range, n samples, dates, 
field_tbl <- read_csv(here::here("data/02_tidied/tidied_field.csv")) #
field_photos <- knitr::include_graphics(here::here("manuscript/figs/supp/field_photos/field_collage.png"))
micro_photos <- knitr::include_graphics(here::here("manuscript/figs/S4_site_micro_photos/micro.png"))
cellct <- include_graphics(here("manuscript/figs/supp/cellct_scatterpie/cellct_scatterpie.png")) # make pies circles circular! they're shightly squished lengthwise
tree_otu <- include_graphics(here("manuscript/supp/figs/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/supp/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/supp/diversity.png"))
depth <- include_graphics(here("manuscript/figs/supp/depth/depth_polished.png")) ###

map_cap <- "Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "Photos of snow algae field sites, arranged from high to low elevation from top to bottom. Alphanumeric code in upper left indicates sample ID."
micro_photo_cap <- "Microphotos of snow algae samples included in sequencing run."
cellct_cap <- "Proportional abundance of snow algae cell morphologies, plotted against date and elevation."
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."
depth_cap <- "A. Representative field photo of snow runnel, with orange on surface and green below. B. Microphoto of orange snow on surface of sample S9.1. C. Microphoto of snow algae below surface of sample S9.1. D. Relative abundance barplot of OTUs in three snow runnels. Sample H2.10 depth and surface samples were taken 1 week apart, other depth/surface pairs are from the same date."
```

## Figures
 1. Map of sample locations
 2. Photos of field sites
 3. Microphotos of snow algae samples
 4. Plots of snow algae 18S community composition. A. All 18S, Silva assignments. B. Chlorophyta assignments with custom reference database.
 5. Maximum likelihood tree of *rbc*L amplicon
 6. Plot of base differences between Genbank 18S and *rbc*L segments
 7. Phylogenetic diversity of snow algae.

@@

```{r, fig.cap=micro_cap}
#scale bar
# # sizes the same (crop template)
# arrange in grid
micro_photos
```

```{r s18_rel_abund, fig.cap=s18_cap}
s18 # should this go in the main fig next to the rbcl assignments?
```

```{r tree, fig.cap=tree_cap}
tree
```

@@

```{r}
field %>% 
   filter(have_seq==T) %>% 
   mutate(notes = if_else(sample_id %in% c("pan18.ro","bre18.rd"), "collected from rock",NA_character_)) %>% 
   select(alias, date, elev_m, lat, lon,color_snow, habitat, notes) %>% 
   arrange(date) %>% 
   kable(caption = table_cap) %>% 
   kable_styling(bootstrap_options = "striped")
```

>>>>

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/supp/map.png")) # crop zoom, city font white, each site gets one point with box specifying elev range, n samples, dates, 
field_tbl <- read_csv(here::here("data/02_tidied/tidied_field.csv")) #
field_photos <- knitr::include_graphics(here::here("manuscript/figs/supp/field_photos/field_collage.png"))
micro_photos1 <- knitr::include_graphics(here::here("manuscript/figs/supp/micro_photos/micro1.png"))
micro_photos2 <- knitr::include_graphics(here::here("manuscript/figs/supp/micro_photos/micro2.png"))
micro_photos3 <- knitr::include_graphics(here::here("manuscript/figs/supp/micro_photos/micro3.png"))

cellct <- include_graphics(here("manuscript/figs/supp/cellct_scatterpie/cellct_scatterpie.png")) # try stacked barplots
tree_otu <- include_graphics(here("manuscript/figs/supp/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/supp/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/supp/diversity.png"))
depth <- include_graphics(here("manuscript/figs/supp/depth/depth_polished.png")) ###

map_cap <- "Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "Photos of snow algae field sites, arranged from high to low elevation from top to bottom. Alphanumeric code in upper left indicates sample ID."
micro_cap <- "Microphotos of snow algae samples included in sequencing run. All scale bars are approximately 20um."
cellct_cap <- "Proportional abundance of snow algae cell morphologies, plotted against date and elevation."
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."
depth_cap <- "A. Representative field photo of snow runnel, with orange on surface and green below. B. Microphoto of orange snow on surface of sample S9.1. C. Microphoto of snow algae below surface of sample S9.1. D. Relative abundance barplot of OTUs in three snow runnels. Sample H2.10 depth and surface samples were taken 1 week apart, other depth/surface pairs are from the same date."
```

## Figures
 1. Map of sample locations
 2. Photos of field sites
 3. Microphotos of snow algae samples
 4. Piecharts of cell count relative abundance, plotted by sample elevation and date
 5. Maximum likelihood tree of *rbc*L amplicon, colored by taxonomic assignment
 6. ML tree of *rbc*L, colored by OTU
 7. Snow algae diversity over time and elevation.
 8. Photos of *Chloromonas krienitzii* above and below the surface, with relative abundance plots at surface and depth.

@@

```{r, fig.cap=micro_cap}
micro_photos1
```

```{r}
micro_photos2
```

```{r}
micro_photos3
```

```{r tree, fig.cap=tree_cap}
tree_otu
```

@@

```{r, fig.cap=depth_cap}
depth
```

```{r}
field_tbl %>% 
   filter(have_seq==T) %>% 
   mutate(notes = if_else(sample_id %in% c("pan18.ro","bre18.rd"), "collected from rock",NA_character_)) %>% 
   select(alias, date, elev_m, lat, lon,color_snow, habitat, notes) %>% 
   arrange(date) %>% 
   kable(caption = table_cap) %>% 
   kable_styling(bootstrap_options = "striped")
```
